Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent

### 2014-09-22 manuscript/paper-tycho.tex
New (smaller) Tycho regions, variant FWHM tables
Add tables with simple model fits and variant FWHM calculation.
Split Tycho regions, compute new FWHMs and fits.
More paper writing.

% This paper
\newcommand*{\tsup}{\textsuperscript}
\newcommand*{\Chandra}{\textit{Chandra}\ }
\newcommand*\mean[1]{\bar{#1}}
\newcommand*{\tsynch}{\tau_{\mt{synch}}}
\newcommand*{\mE}{m_\mathrm{E}}
\defcitealias{ressler2014}{R14}

@@

% Intro -- shocks, DSA, thin rims, filament observations; other fields/work
Forward shock accelerated ISM/CSM particles in young supernova remnants emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream \citep{koyama1995, reynolds1996}, producing a shell-like
morphology with bright X-ray and radio rims/filaments due to line-of-sight
projection (hereafter, thin rims).
Seminal observations \& interpretations of these filaments, interpretation in
context of DSA.  Attempts to model filaments and figure out what's going on.
Why do we care about these models?  They tell us something about what happens
behind the shock, and perhaps what's going on at the shock.  We get at the
plasma turbulence, magnetic field turbulence and structure, electron injection.
Applications to: cosmic ray acceleration, turbulent field amplification, (note
assumptions in re proton/electron spectra).
Cut-off energy of injected
electrons?  Relevant to, broadly, all astrophysical shocks: Earth's bow shock,
PWNe, SNe and/or stellar wind blown bubbles, starbursts \citep{heckman1990},
AGN jets, galaxy clusters \citep{van-weeren2010}, and even cosmological shocks
\citep{miniati2000, ryu2008}.  See relevant reviews \citep{blandford1987}.

@@

% Which one is right?
Previous measurements of basic observables \citep[e.g.,][]{bamba2003,
bamba2005-hist, bamba2005-vela, parizot2006} and consequences.  Conclusion that
magnetic fields are amplified according to loss-limited model.  How?  Field
amplification from plasma instabilities, evidence for stronger compression ratios?
\citep{blondin2001}.  Lots of numerical and theoretical work that I don't
understand.

Introduce $\tsynch$ and the basic intuition.
Explain why diffusion is an important consideration
(when did this start being recognized as relevant?).

Previous work that accounted for advection/diffusion alone or separately,
previous work that considered both simultaneously (as we do here).

But, magnetic damping offers a tantalizing alternate explanation and has not
been fully tested.  Equivocal results by \citet{araya2010} for Cas A.
\citet{rettig2012} proposed discriminating based on filament spectra -- the
expectation is that damped spectra are softer, loss-limited harder.
\citet{ressler2014} developed the idea of investigating energy dependence and
found rim narrowing in the remnant of SN 1006, strongly favoring a loss-limited
model.

% Why Tycho's SNR
To test these models, we turn to the filaments of Tycho's supernova remnant
(hereafter, Tycho).
Like all historical SNe, Tycho is close enough that we can spatially
resolve these rims with \Chandra and say something useful.  Like SN 1006, Tycho
has well defined synchrotron rims associated with expansion into a low-density
ISM.  \citet{williams2013} favor mean pre-shock ISM density $\abt 0.1$--$0.2
\unit{cm^{-3}}$ from \textit{Spitzer} observations of shocked ISM dust
emission, consistent with Tycho's X-ray expansion rate \citep{katsuda2010}; SN
1006, by comparison, has pre-shock density $\abt 0.01$--$0.1 \unit{cm^{-3}}$ at
its nonthermal NE, SW limbs \citep{acero2007}.
\note[Aaron]{More disjointed}
Mention molecular cloud interaction \citep{reynoso1999}? Maybe below in region
selection as well.
Previous estimates of Tycho fields/diffusion (something similar to Sean's table
for SN 1006?).  CR acceleration (aside: \citet{eriksen2011}) evidence in Tycho,
if relevant.

% Paper roadmap
\note[Aaron]{roadmap}
We measure Tycho's rim widths, following the work of \citet{ressler2014}
(hereafter, \citetalias{ressler2014}) in the remnant of SN 1006.
We make measurements to distinguish between two main scenarios
(explain how diffusion/advection competition come into this).
Our procedure, in both measurement and rim width modeling, follows that of
\citetalias{ressler2014} with only slight modifications.
We first select regions around Tycho's forward shock for analysis, measure
rim widths, and verify that rim spectra are free of thermal line emission.
Using two models for particle transport, we fit measured widths...
We discuss the implications of our fits and models for magnetic shock
amplification (lending credence to previous estimates, in disfavoring magnetic
field amplification), and discuss particle diffusion/acceleration at the shock.
Any further misc. applications (constraints on precursors, etc).

@@

A first approximation is to let electrons have constant energy that is dumped
catastrophically after a synchrotron timescale $\tsynch = 1/(b B^2 E)$, where
$b = 1.57 \times 10^{-3}$ in CGS units and $B$ is magnetic field (which may
vary as $B=B(x)$.  The sink term is $C = -f / \tsynch$, yielding:
\begin{equation} \label{eq:simp-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
    \frac{f}{\tau_{\mt{synch}}} = 0
\end{equation}
which is equation (5) of \citetalias{ressler2014}.
\note[Aaron]{I think there should be a delta function for e- injection, but it
probably doesn't affect the solution.  Double check.}
Conveniently, equation~\eqref{eq:simp-mod} has analytic solution $f \propto
\exp(-x/a)$ where $a$ is a characteristic scale length.  The full width half
maximum (FWHM) of a thin rim produced by this ``simple'' model is given by:
\begin{equation} \label{eq;simp-fwhm}
    w = \frac{2\beta D / v_d}{\sqrt{1 +\frac{4D}{v_d^2 \tsynch}} - 1}
\end{equation}
where $\beta$ is a projection factor relating $w$ to $a$ as $w = \beta a$.  We
take $\beta = 4.6$ assuming projection from spherical shell, as derived by
\citet{ballet2006}.

A more advanced model is given by accounting for continuous radiation energy
losses while electrons are transported downstream:
\begin{equation} \label{eq:full-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =
    K_0 E^{-s} e^{-E/E_{\mt{cut}}} \delta(x) + \frac{\ptl}{\ptl E}
      \left(bB^2E^2f\right)
\end{equation}
which is equation (12) of \citetalias{ressler2014}.  The injected electron
distribution is an exponentially cut-off power law with normalization $K_0$ and
cut-off energy $E_{\mt{cut}}$; the expression for the cut-off energy is
determined by the form of the diffusion coefficient $D$, which we discuss in
Section~\ref{sec:diffcoeff}.  To determine rim profiles and widths, we
numerically solve for electron distribution $f(E,x)$ using Green's function
solutions due to \citet{lerche1980} and \citet{rettig2012}; the equations are
given using notation close to that of this paper by \citetalias{ressler2014}.
The electron distribution may then be integrated to obtain synchrotron
emissivity:
\begin{equation} \label{eq:emissivity}
    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
\end{equation}
where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is one-particle synchrotron
emissivity with $K_{5/3}(z)$ a modified Bessel function of the second kind
\citep{pacholczyk1970}.  Integrating emissivity over lines of sight for a
spherical shell yields intensity:
\begin{equation} \label{eq:intensity}
    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
                    j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
\end{equation}
where $s$ is the line-of-sight coordinate.  We can then compute these
integrals (equations~\eqref{eq:emissivity},~\eqref{eq:intensity}) to obtain
model predictions for rim FWHMs.

@@

@@

Bohm diffusion: $D(E) = \eta C_d E / B$. Generalized diffusion writen as:
\begin{equation}
    D(E) = \eta C_d E^\mu / B = \eta_h D(E_h) (E/E_h)^\mu
\end{equation}
Explain the use of fiducial energy -- this makes sense and eases discussion,
but linking $E_h$ and $\eta_2$ to $\eta$ and plain Bohm diffusion seems a bit
murky.

Mention that different $\mu$ values arise from particular models of turbulence.

We use an electron spectrum cut-off energy of:
\begin{align*}
    E_{\mt{cut}} =
        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \unit{\mu G}}\right)^{-1/(1+\mu)} \\
        &\times \left(\frac{v_s}{10^8 \unit{cm/s}}\right)^{2/(1+\mu)}
        \left[
            \frac{E_h^{\mu - 1}}{\eta}
        \right]^{1 / (1 + \mu)}
\end{align*}
which is equation~(19) of \citetalias{ressler2014}.
\note[Aaron]{This differs from Sean's presentation -- I drew this from the
Fortran code and it looks consistent w/ Parizot et al., but I haven't vetted
the prefactor $8.3 \unit{TeV}$.  And, I have an extra exponent $\mu - 1$ on the
$E_h$ ?!  Come back to this shortly.}

@@

We also consider (not really) a magnetically damped field of form
\begin{equation}
    B(x) = B_{\mt{min}} + \left(B_0 + B_{\mt{min}}\right) \exp\left(-x / a_b\right) ,
\end{equation}
following \citetalias[Section 3.2]{ressler2014} and \citet{pohl2005}.

@@

All measured rim widths are at least $\abt 1\arcsec$ and hence are resolved by
\textit{Chandra}'s point-spread function.
Looking at proposer's guide, Figure 4.13 -- the off-axis PSF should
still have FWHM of $\abt 1\arcsec$ at $4\arcmin$ (approx. Tycho's radius).
Is that good enough for us?
(Cassam-Chena\"i et al. considered PSF effects when modeling rim widths, though
it doesn't look like it made a big difference?)

@@

% NOTE keep mentioned number of regions updated!
% TODO regions 2,3; 6,7 should be stretched forward a little more in regions-5
%      just to be more consistent (just from eyeballing...)
We obtained radial intensity profiles from $\abt 10$--$20\arcsec$ behind the
shock to $\abt 2$--$8\arcsec$ in front for each of our 13 regions in all five
energy bands.  To increase signal-to-noise, we integrate along the shock ($\abt
8$--$24\arcsec$) in each region.  Plotted and fitted profiles are reported in
vignetting and exposure-corrected, but arbitrary, intensity units; error bars
are computed from raw count data assuming Poisson statistics.  Intensity
profiles peak sharply (within $\abt 2$--$3\arcsec$) behind the shock,
demarcating our thin rims, and then fall off until thermal emission from ejecta
picks up at Tycho's contact discontinuity \citep{warren2005}.

@@

To estimate FWHM uncertainties, we horizontally stretched each best-fit
profile by mapping radial coordinate $x$ to
$x'(x) = x (1 + \xi (x-x_0)/(50\arcsec-x_0))$ with $\xi$ an arbitrary stretching
parameter and $x_0$ the best-fit rim center from equation~\eqref{eq:prof};
this yields a new profile $h'(x) = h(x'(x))$.
We varied $\xi$ (and hence rim FWHM) to vary each profile fit $\chi^2$ by 2.7
and the stretched or compressed FWHMs as upper/lower bounds on our reported
FWHMs.

@@

% Model knobs and how we twiddled them
We have three parameters to vary (more if we consider magnetic damping):
diffusion-energy scaling exponent $\mu$, normalized diffusion
coefficient $\eta_2$, and magnetic field strength $B_0$.
To make our nonlinear fitting tractable, we fix $\mu$ in all fits and
consider $\mu = 0$, 1/3, 1/2, 1, 1.5, and 2; recall that $\mu = 1/3$ and $1/2$
respectively correspond to predictions from Kolmogorov and Kraichnan turbulent
energy spectra.  As $\eta_2$ is highly variable in our fits, we also consider
fits with $\eta_2 = 1$ fixed, coincident with Bohm diffusion at $2 \unit{keV}$.

@@

% How to do the fit
Our data are readily fit to the simple model by equation~\eqref{eq:simp-width}.
The full model is numerically computed as detailed in
Section~\ref{sec:transport}, yielding intensity profiles and hence model FWHMs
in each energy band.
For least squares fitting purposes, the full model is treated as a black box
that takes in physical parameters
% TODO modify tables to match what is stated here -- in regards to parameters
% being effectively unbounded.
% TODO for extreme values in tables -- go back and double check chi^2 space
To perform full model fits, we tabulated a large grid for fixed values of $\mu$
and shock velocity $v_s$.  If any fit runs to $\eta_2 = 10^5$ or $B_0 = 10
\unit{mG}$, we deem it effectively unconstrained (only a few fits do so, and
only to the $\eta_2$ limit).  Note that we do not allow / consider fits with
$\eta_2$ negative (may be trivial, just note parameter bounds).  As the full
continuous loss model must be numerically solved, its predicted rim widths are
subject to resolution error in the numerical integrals.  We chose our
integration resolutions such that the fractional error associated with
halving/doubling our resolution is less than $1\%$ for the parameter space
relevant to our filaments.
\note[Aaron]{rewrite -- unclear.  Need to verify
1\% claim and check Pacholczyk table resolution (and possibly Bessel
function numbers)...}

@@

In Table~\ref{tab:fwhms} we report FWHM measurements for all of our regions.
As previously noted, we could not resolve FWHMs for some regions in the
0.7--1 keV band.  We also report $\mE$ values for all but the lowest energy
band, computed point-to-point as $\mE(E_2) = \ln(w_2/w_1) / \ln(E_2/E_1)$ where
$w_1, w_2$ and $E_1, E_2$ are FWHMs and lower energy values for each energy
band (e.g., $\mE(\text{1 keV}) = \ln(w(\text{1-1.7 keV}/w(\text{0.7-1 keV})) /
\ln(\text{1 keV}/\text{0.7 keV})$ is computed from widths/energies.  Although
the values of $\mE$ reflect a good deal of variability in the underlying width
measurements, we see that most regions and energy bands display a decrease in
rim widths as a function of energy.

@@

Here we have presented $\mE$ to demonstrate the fall-off of rim width energy.
However, we emphasize that $\mE$ is currently not factored into our subsequent
analysis.

@@

% NOTE keep updated -- for which region are we giving simple and full fits?
We find that the simpler catastrophic dump model (equation~\eqref{eq:simp-mod})
produces the same qualitative trends seen in the full continuous energy loss
model.
The first row of Table~\ref{tab:fits} compares simple and full model fits for
Region 1.
The key differences are \emph{blah}.  The errors are comparable, the parameters
are comparable but shifted by X amount; this is consistent in all filaments?
(details tbd).
Consequently, we present only the full model fits for all other
filaments in Table~\ref{tab:fits}.  However, the simple model is useful for
building intuition and we will refer to its results in the following discussion
(?); \citetalias{ressler2014} also give examples of simple model fits in SN
1006 \note[Aaron]{sentence maybe unnecessary}.

% Individual region fit results
Table~\ref{tab:fits} presents full model fit results for all regions
considered. Errors are computed by varying free parameters $B_0$,
$\eta_2$ to obtain $\Delta\chi^2 = 1$, corresponding to $1$-$\sigma$ confidence
limits on our fit parameters.
\begin{table}[ht]
    \tiny
    \centering
    \caption{Full model best fits for individual regions, Filament 1.
    \label{tab:fits}}
    \input{tab-fits-all.tex}
\end{table}

@@

Explain briefly, effects (percentage change or similar?) of model fit parameter
changes, results if we vary Tycho distance to $2.3 \unit{kpc}$ or $4
\unit{kpc}$; see \citet{hayato2010}.

Is it worth discussing effects of various twiddle-ables: compression ratio $r$,
accounting for azimuthal variation in $v_s$ (compare to taking a remnant
average)?  Sean already discussed $E_{\mt{cut}}$ (result: more high energy
elections to damp out widening effect at high energy).

(YES, ADD THIS TO DRAFT -- MAY AS WELL)

Any azimuthal variations -- need the table of filament averaged parameters
first, and possibly smaller regions.

>>>>

% This paper
\newcommand*{\tsup}{\textsuperscript}
\newcommand*{\Chandra}{\textit{Chandra}\ }
\newcommand*\mean[1]{\bar{#1}}
\newcommand*{\tsynch}{\tau_{\mt{synch}}}
\newcommand*{\mE}{m_\mt{E}}
\newcommand*{\Ecut}{E_{\mt{cut}}}
\defcitealias{ressler2014}{R14}

@@

% Intro -- shocks, DSA, thin rims, filament observations; other fields/work
Forward shock accelerated ISM/CSM particles in young supernova remnants emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream \citep{koyama1995, reynolds1996}, producing a shell-like
morphology with bright X-ray and radio rims/filaments due to line-of-sight
projection (hereafter, thin rims).
Seminal observations \& interpretations of these filaments, interpretation in
context of DSA.  Attempts to model filaments and figure out what's going on.
Why do we care about these models?  They tell us something about what happens
behind the shock, and perhaps what's going on at the shock.  We get at the
plasma and magnetic field turbulence, electron injection.
Applications to: cosmic ray acceleration, turbulent field amplification, (note
assumptions in re proton/electron spectra).
Cut-off energy of injected electrons?
Relevant to, broadly, all astrophysical shocks: Earth's bow shock,
PWNe, SNe and/or stellar wind blown bubbles, starbursts \citep{heckman1990},
AGN jets, galaxy clusters \citep{van-weeren2010}, and even cosmological shocks
\citep{miniati2000, ryu2008}.  See relevant reviews \citep{blandford1987}.

@@

% Which one is right?
Which mechanisms are most relevant to historical SNRs?
\note[Aaron]{need to read more / more thoroughly}
Introduce $\tsynch$ and the basic intuition. Explain why diffusion is important
(when did diffusion start being recognized as relevant to SNR filaments? or how was
this shown?).
Following Sean (i.e., taking all of his references), relevant previous
observational studies.
\citet{bamba2003, vink2003, yamazaki2004, ballet2006} consider advection and
diffusion separately (with the break-point at $\Ecut$ when advective and
diffusive length scales are equal;
\citet{parizot2006, araya2010} consider diffusion and advection simultaneously
with the catastrophic dump equation.
\citet{berezhko2003, berezhko2004, cassam-chenai2007, morlino2010, rettig2012}
consider diffusion and advection simultaneously with the continuous loss
equation instead.
Conclusion that magnetic fields are amplified according to loss-limited model.  How?  Field
amplification from plasma instabilities, evidence for stronger compression ratios?
\citep{blondin2001}.  Lots of numerical and theoretical work that I don't
understand.
\citet{rettig2012} mention independent estimates of magnetic field, from
\citet{acero2010, acciari2011} for SN 1006 and Tycho (considering gamma-ray,
radio, X-ray data).

Magnetic damping offers a tantalizing alternate explanation and has not
been fully tested.  Equivocal results by \citet{araya2010} for Cas A.
\citet{rettig2012} gave model predictions for several historical SNRs and
proposed discriminating based on filament spectra -- the
expectation is that damped spectra are softer, loss-limited harder.
\citet{ressler2014} developed the idea of investigating energy dependence and
found rim narrowing in the remnant of SN 1006, strongly favoring a loss-limited
model.

% Why Tycho's SNR
To further test these models, we turn to the remnant of Tycho's 1572 supernova
(hereafter, Tycho).  Tycho, being a nearby galactic SNR, is close enough that
its rims are well-resolved by \textit{Chandra}'s spatial resolution.  Tycho has
an extensive and unusually contiguous shell of synchrotron rims around its
periphery, consistent with expansion into a low density ISM; ISM.
\citet{williams2013} favor mean pre-shock ISM density $\abt 0.1$--$0.2
\unit{cm^{-3}}$, consistent with Tycho's X-ray expansion rate
\citep{katsuda2010}.  Although Tycho is expanding into an ISM gradient
\citep{williams2013} and interacting with a molecular cloud on its eastern limb
\citep{reynoso1999}, Tycho's spherical morphology suggests that we might expect
more consistent shock acceleration around its periphery than in other
historical remnants, whether of Type Ia or CC SNe \note[Aaron]{this is not really
justifiable, but I think it's worth noting something to this effect?}.
CR acceleration evidence in Tycho, if relevant? \citet{eriksen2011,
acciari2011}.

% Paper roadmap
\note[Aaron]{roadmap}
We measure Tycho's rim widths, following the work of \citet{ressler2014}
(hereafter, \citetalias{ressler2014}) on the remnant of SN 1006.
We make measurements to distinguish between two main scenarios
(explain how diffusion/advection competition come into this).
Our procedure, in both measurement and rim width modeling, follows that of
\citetalias{ressler2014} with only slight modifications.
We first select regions around Tycho's forward shock for analysis, measure
rim widths, and verify that rim spectra are free of thermal line emission.
Using two models for particle transport, we fit measured widths...
We discuss the implications of our fits and models for magnetic shock
amplification (lending credence to previous estimates, in disfavoring magnetic
field amplification), and discuss particle diffusion/acceleration at the shock.
Any further misc. applications (constraints on precursors, etc).

@@

A first approximation is to let electrons have constant energy that is dumped
catastrophically after a synchrotron timescale $\tsynch = 1/(b B^2 E)$, where
$b = 1.57 \times 10^{-3}$ in CGS units and $B$ is magnetic field (which may
vary as $B=B(x)$).  The sink term is $C = -f / \tsynch$, yielding:
\begin{equation} \label{eq:simp-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
    \frac{f}{\tau_{\mt{synch}}} = 0
\end{equation}
which is equation (5) of \citetalias{ressler2014}.
\note[Aaron]{I think there should be a delta function for e- injection, but it
probably doesn't affect the solution.  Double check.}
Conveniently, equation~\eqref{eq:simp-mod} has analytic solution $f \propto
\exp(-x/a)$ where $a$ is a characteristic scale length.  The full width half
maximum (FWHM) of a thin rim produced by this ``simple'' model is given by:
\begin{equation} \label{eq:simp-fwhm}
    w = \frac{2\beta D / v_d}{\sqrt{1 +\frac{4D}{v_d^2 \tsynch}} - 1}
\end{equation}
where $\beta$ is a projection factor relating $w$ to $a$ as $w = \beta a$.  We
take $\beta = 4.6$ assuming projection from spherical shell, as derived by
\citet{ballet2006}.

A more advanced model is given by accounting for continuous radiation energy
losses while electrons are transported downstream:
\begin{equation} \label{eq:full-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =
    K_0 E^{-s} e^{-E/\Ecut} \delta(x) + \frac{\ptl}{\ptl E}
      \left(bB^2E^2f\right)
\end{equation}
which is equation (12) of \citetalias{ressler2014}.  The injected electron
distribution is an exponentially cut-off power law with normalization $K_0$ and
cut-off energy $\Ecut$; the cut-off energy is determined by the form of the
diffusion coefficient $D$, which we discuss in
Section~\ref{sec:diffcoeff}.  To determine rim profiles and widths, we
numerically solve for electron distribution $f(E,x)$ using Green's function
solutions due to \citet{lerche1980} and \citet{rettig2012}; the equations are
given using notation close to that of this paper by \citetalias{ressler2014}.
The electron distribution may then be integrated to obtain synchrotron
emissivity:
\begin{equation} \label{eq:emissivity}
    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
\end{equation}
where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is one-particle synchrotron
emissivity with $K_{5/3}(z)$ a modified Bessel function of the second kind
\citep{pacholczyk1970}.  Integrating emissivity over lines of sight for a
spherical shell yields intensity:
\begin{equation} \label{eq:intensity}
    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
                    j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
\end{equation}
where $s$ is the line-of-sight coordinate.  We can then compute these
integrals (equations~\eqref{eq:emissivity},~\eqref{eq:intensity}) to obtain
model predictions for rim FWHMs.

In what follows we consider both transport models, but primarily present
results from the more advanced model (equation~\eqref{eq:full-mod}) as we find
the qualitative behavior of both models is comparable.

@@

The modus operandi of previous work has been to assume Bohm diffusion, or at
least Bohm diffusion-energy scaling.  Bohm diffusion makes the
assumption that particle mean free path, and hence the diffusion coefficient,
is proportional to the particle gyroradius, yielding $D \propto E$.

\citet{reynolds2004} suggested that physically motivated models of MHD
turbulence could give rise to non-linear diffusion-energy scalings, assuming
quasi-linear turbulence \note[Aaron]{read more}.
Specifically, power-law energy-wavenumber spectra for Kolmogorov and Kraichnan
turbulence predict $D \propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.

We consider a generalized diffusion coefficient that allows arbitrary
power-law dependence of diffusion upon energy:
\begin{equation} \label{eq:diffcoeff}
    D(E) = \eta C_d E^\mu / B = \eta_h D(E_h) (E/E_h)^\mu
\end{equation}
As the diffusion coefficient is energy dependent, we rewrite the diffusion
coefficient in terms of a fiducial energy $E_h = 2 \unit{keV}$ throughout, with
$\eta_2 = \eta_h$.  The constant $\eta_2$ is the diffusion coefficient at
$2 \unit{keV}$ scaled by the Bohm diffusion value.
\note[Aaron]{Also give some intuition of relation of $D$ and $\Ecut$ to relate to
previous studies.}

@@

With a diffusion coefficient in hand, we determine the electron spectrum
cut-off energy by equating synchrotron loss and acceleration timescales;
the acceleration timescale is determined from the theory of diffusive shock
acceleration.  The cut-off energy, following \citet{parizot2006}, is given as:
\begin{align*}
    \Ecut =
        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \unit{\mu G}}\right)^{-1/(1+\mu)} \\
        &\times \left(\frac{v_s}{10^8 \unit{cm/s}}\right)^{2/(1+\mu)}
        \left[
            \frac{E_h^{\mu - 1}}{\eta}
        \right]^{1 / (1 + \mu)}
\end{align*}
\note[Aaron]{This differs from Sean's presentation -- I drew this from the
Fortran code and it looks consistent w/ Parizot et al., but I haven't vetted
the prefactor $8.3 \unit{TeV}$.  And, I have an extra exponent $\mu - 1$ on the
$E_h$ ?!  Come back to this shortly.}

@@

We also consider (not really) a magnetically damped field of form
\begin{equation}
    B(x) = B_{\mt{min}} + \left(B_0 + B_{\mt{min}}\right) \exp\left(-x / a_b\right) ,
\end{equation}
following \citetalias[Section 3.2]{ressler2014} and \citet{pohl2005}.
\note[Aaron]{Look over \citet{marcowith2010}.}

Set up the calculation w/ a range of scale lengths (with $B_0$,
$\eta_2$ chosen so that damping is the dominant control for $0.7$--$7
\unit{keV}$), and compute FWHMs and $\mE$ values?

\subsection{Previous studies of Tycho}

\note[Aaron]{Should we follow \citet{ressler2014} in adding a table of prior
magnetic field estimates?  I am uncertain of where to review previous
literature -- introduction gives more direct motivation and context, putting
before or in-line w/models allows us to explain who used what.  Putting
before/after model exposition, keeps all the numbers/explanation of previous
work in one place -- also easier to pull in discussion of other
methods/attacks.  Right now text is rather disjointed.}
\citet{parizot2006} derive magnetic fields of $300$--$500 \unit{\mu G}$; they
also give both diffusion coefficients (in their $k_0$?) and $\Ecut$ values.
\citet{rettig2012} used a measured filament lengthscale and considered
loss-limited and magnetic damping models separately for several historical
SNRs.  For Tycho: they report $B = 310 \unit{\mu G}$ with $\Ecut = 24
\unit{TeV}$; since $\Ecut$ is set by balancing advective/diffusive
lengthscales, this is equivalent to our reporting of a diffusion coefficient
(?).  With magnetic damping, they report $B = 150 \unit{\mu G}$ and a larger
$\Ecut = 34 \unit{TeV}$.  Taken from \citet{rettig2012}: \citet{acciari2011}
give $80$, $230 \unit{\mu G}$ for leptonic/hadronic models for gamma-ray
emission in Tycho.

@@

All measured rim widths are at least $\abt 1\arcsec$ and hence are resolved by
\textit{Chandra}'s point-spread function.
Looking at proposer's guide, Figure 4.13 -- the off-axis PSF should
still have FWHM of $\abt 1\arcsec$ at $4\arcmin$ (approx. Tycho's radius).
Is that good enough for us?
(Cassam-Chena\"i et al. considered PSF effects when modeling rim widths, though
it doesn't look like it made a big difference?)
If the PSF matters, this favors some combination of stronger
magnetic fields and weaker diffusion.

@@

% NOTE keep mentioned number of regions updated!
% TODO regions 2,3; 6,7 should be stretched forward a little more in regions-5
%      just to be more consistent (just from eyeballing...)
% Update these numbers before final version.
We obtained radial intensity profiles from $\abt 10$--$20\arcsec$ behind the
shock to $\abt 2$--$8\arcsec$ in front for each of our 13 regions in all five
energy bands.  To increase signal-to-noise, we integrate along the shock ($\abt
8$--$24\arcsec$) in each region.  Plotted and fitted profiles are reported in
vignetting and exposure-corrected, but arbitrary, intensity units; error bars
are computed from raw count data assuming Poisson statistics.  Intensity
profiles peak sharply (within $\abt 2$--$3\arcsec$) behind the shock,
demarcating our thin rims, and then fall off until thermal emission from ejecta
picks up at Tycho's contact discontinuity \citep{warren2005}.

@@

To estimate FWHM uncertainties, we horizontally stretched each best-fit
profile by mapping radial coordinate $x$ to
$x'(x) = x (1 + \xi (x-x_0)/(50\arcsec-x_0))$ with $\xi$ an arbitrary stretching
parameter and $x_0$ the best-fit rim center from equation~\eqref{eq:prof};
this yields a new profile $h'(x) = h(x'(x))$.
We varied $\xi$ (and hence rim FWHM) to vary each profile fit $\chi^2$ by 2.7
and the stretched or compressed FWHMs as upper/lower bounds on our reported
FWHMs. \note[Aaron]{Unimportant note: chi-squared values from our
fits assume that input errors are 1-sigma.  But, taking $\Delta\chi^2 = 1$
for our FWHM errors would shrink the errors even further, and the errors
don't reflect uncertainty that may arise from, e.g., using different fit
functions or taking different profiles.}

@@

% Model knobs and how we twiddled them
We varied three physical parameters (more if we consider magnetic damping):
diffusion-energy scaling exponent $\mu$, normalized diffusion
coefficient $\eta_2$, and magnetic field strength $B_0$.
To make nonlinear fitting tractable, we fixed $\mu$ in all fits and considered
$\mu = 0$, $1/3$, $1/2$, $1$, $1.5$, and $2$;
recall that $\mu = 1/3$ and $1/2$ correspond to Kolmogorov and Kraichnan turbulence.
As $\eta_2$ is highly variable in our fits, we also performed
fits with $\eta_2 = 1$ fixed, coincident with Bohm diffusion at $2 \unit{keV}$.

@@

% How to do the fit
Equation~\eqref{eq:simp-fwhm} was directly fit to our measurements to obtain
best-fit values of $\eta_2$ and $B_0$.
The full model was numerically computed as detailed in
Section~\ref{sec:transport}, yielding intensity profiles and hence model FWHMs
in each energy band; we then varied the input parameters ($\eta_2$, $B_0$) to
obtain a least squares best fit.
To assist the nonlinear fitting, we tabulated a large grid of model FWHM values
for various values of $\mu$ and shock velocity $v_s$; from a best initial grid
value, we then used a Levenberg-Marquardt fitting routine to determine the best
fits.
For both simple and full fits, we deemed fits with $\eta_2 \geq 10^5$ and $B_0
\geq 10 \unit{mG}$ effectively unconstrained; $\eta_2$ is also constrained to
be positive .

% TODO modify tables to match what is stated here -- in regards to parameters
% being effectively unbounded.
% TODO for extreme values in tables -- go back and double check chi^2 space
As the full model must be numerically solved, its predicted rim widths are
subject to resolution error in the numerical integrals.  We chose our
integration resolutions such that the fractional error in model FWHMs
associated with halving/doubling integration resolution is less than $1\%$ for
the parameter space relevant to our filaments.
\note[Aaron]{rewrite -- unclear.  Need to verify 1\% claim and check Pacholczyk
table resolution (and possibly Bessel function numbers)...}

@@

In Table~\ref{tab:fwhms} we report FWHM measurements for all of our regions.
As previously noted, we could not resolve FWHMs for some regions in the 0.7--1
keV band.  We also report $\mE$ values for all but the lowest energy band,
computed point-to-point as: \begin{equation} \mE(E_2) =
\frac{\ln(w_2/w_1)}{\ln(E_2/E_1)} \end{equation} where $w_1, w_2$ and $E_1,
E_2$ are FWHMs and lower energy values for each energy band (e.g., $\mE$ at $1
\unit{keV}$ is computed using FWHMs from $0.7$--$1 \unit{keV}$ and $1$--$1.7
\unit{keV}$, and taking $E_2 = 1 \unit{keV}$ and $E_1 = 0.7 \unit{keV}$.
Although the values of $\mE$ reflect a good deal of variability in the
underlying width measurements, we see that most regions and energy bands
display a decrease in rim widths as a function of energy.  NOTE (draft): we
emphasize that $\mE$ is currently not considered or utilized in our subsequent
analysis.

@@

@@

% NOTE keep updated -- for which region are we giving simple and full fits?
We find that the simpler catastrophic dump model (equation~\eqref{eq:simp-mod})
produces the same qualitative trends seen in the full continuous energy loss
model.  The first row of Table~\ref{tab:fits} compares simple and full model fits for
Region 1.  In general, simple model fits are less poorly constrained (i.e.,
fits are more likely to reach manual fitting limits).
Where both simple and full model fits are well constrained (i.e., moderate to
small $\eta_2$ values), the simple model favors slightly smaller $\eta_2$ and
slightly larger $B_0$.  But this is not always true, and it is difficult to
identify any obvious trends as both fits are quite variable across $\mu$ values
and different regions.
\note[Aaron]{from the table calculations, the simple model needed larger $B_0$
values than the full model for a fixed $\eta_2$ and mean width (roughly
speaking); this effect strengthened with larger $\eta_2$.  We're looking at
order 10--50\% effects}.
For the rest of our results and discussion, we consider only full model fits.

% Individual region fit results
Table~\ref{tab:fits} presents full model fit results for all regions
considered. Errors are computed by varying free parameters $B_0$,
$\eta_2$ to obtain $\Delta\chi^2 = 1$, corresponding to $1$-$\sigma$ confidence
limits on our fit parameters.
In Figure~\ref{fig:fits-all} we also plot the best full model fits for the same
regions tabulated in Table~\ref{tab:fits}

\begin{table}[ht]
    \tiny
    \centering
    \caption{Full model best fits for individual regions, Filament 1.
    \label{tab:fits}}
    \input{tab-fits-all.tex}
\end{table}

@@

Discuss, briefly, effects of twiddle-ables: changing Tycho distance ($2.3
\unit{kpc}$ to $4 \unit{kpc}$, see \citet{hayato2010}), compression ratio $r$,
accounting for azimuthal variation in $v_s$ (compare to taking a remnant
average?).  Sean already discussed $\Ecut$ (result: more high energy electrons
to damp out narrowing at high energy, if $\Ecut$ not included).
